### 2018-07-09 acros.tex

\newacronym{ADS}{ADS}{Accelerator-Driven Systems}

@@

\newacronym{ASTRID}{ASTRID}{Advanced Sodium Technological Reactor for Industrial Demonstration}

@@

\newacronym{BWR}{BWR}{Boiling Water Reactor}

@@

@@

\newacronym{EPR}{EPR}{European Pressurized Reactor}

@@

\newacronym{FP}{FP}{Fission Products}

@@

\newacronym{MOX}{MOX}{Mixed Oxide Fuel}

@@

@@

\newacronym{MWe}{MWe}{Mega Watt electric}

@@

@@

\newacronym{PHWR}{Pressurized Heavy Water Reactor}{Pressurized Heavy Water Reactor}

@@

@@

\newacronym{UNF}{UNF}{Used Nuclear Fuel}
\newacronym{UOX}{UOX}{Uranium Oxide Fuel}

>>>>

@@

@@

@@

\newacronym{CFD}{CFD}{Computational Fluid Dynamics}

@@

\newacronym{EPR}{EPR}{European Pressurized Reactors}

@@

\newacronym{FP}{FP}{Fission Product}

@@

\newacronym{MOSART}{MOSART}{Molten Salt Actinide Recycler and Transmuter}
\newacronym{MOX}{MOX}{mixed oxide}
\newacronym{MPI}{MPI}{Message Passing Interface}

@@

\newacronym{MSFR}{MSFR}{Molten Salt Fast Reactor}

@@

@@

\newacronym{NPP}{NPP}{Nuclear Power Plant}

@@

@@

\newacronym{REE}{REE}{rare earth element}

@@

\newacronym{UOX}{UOX}{uranium oxide}

### 2018-07-09 introduction.tex
.gitignore is now working

Thorium-fueled \gls{MSBR}-like reactors similar to the one in this thesis are described in (6, 7, 8, 9). Nevertheless, most of these efforts considered only simplified unit-cell geometry because depletion computations for a many-year fuel cycle are computationally expesive even for simple models.

@@

The \gls{MSBR} complex geometry is hard to describe in software input, and, usually, researchers make significant geometric simplifications to model it \cite{park_whole_2015}. Note that this thesis leverages extensive computational resources to avoid these geometric approximations and accurately capture breeding behavior. This article only discusses liquid-fueled \glspl{MSR}. Discussions of \glspl{MSR} herein refer only to the liquid-fueled variants. Another challenge of the \glspl{MSR}, its delayed neutron precursor drift related to circulating liquid fuel, is not treated here.

>>>>

Thorium-fueled \gls{MSBR}-like reactors similar to the one in this work are described in (6, 7, 8, 9). Nevertheless, most of these efforts considered only simplified unit-cell geometry because depletion computations for a many-year fuel cycle are computationally expesive even for simple models.

@@

The \gls{MSBR} complex geometry is hard to describe in software input, and, usually, researchers make significant geometric simplifications to model it \cite{park_whole_2015}. Note that this study leverages extensive computational resources to avoid these geometric approximations and accurately capture breeding behavior. This article only discusses liquid-fueled \glspl{MSR}. Another challenge of the \glspl{MSR}, its delayed neutron precursor drift related to circulating liquid fuel, is not treated here.
